\input{files/cfg.tex}
\input{files/codebookSet.tex}

\section{\Jlabel{file}{desc.tcl}}

A description file for a system. A typical file looks like:

\input{files/desc.tex}

{\tt  desc.tcl} also is   a good  place    to re-define other   common
functions such as {\tt  dbaseUttFilter} or {\tt hmmMakeUtterance}.  In
principle, you are free to re-configure everything  in this script, it
is however common  practice, to set  the Tcl-variable {\tt SID} to the
name  of  the directory, in which   this incarnation of {\tt desc.tcl}
resides.

\input{files/dictionary.tex}
\input{files/distribSet.tex}
\input{files/distribTree.tex}
\input{files/featAccess.tex}
\input{files/featDesc.tex}

\section{\Jindex{.janusrc}} \label{file:.janusrc}

This  describes the    file \Jindex{.janusrc},   which  is the    main
configuration file  for Janus.  A copy of  this file  can be  found in
\texttt{\~{ }/janus/scripts/janusrc}. It is  usable for both OSs, Unix
and Windows.

\input{files/janusrc.tex}

It is read by JANUS at start-up. You'll then have to set your environment
variables correctly. Just for reference, my \texttt{.tcshrc} contains
the following Janus-related entries:

{\small
\begin{verbatim}
# For Janus:
setenv JANUS_LIBRARY $HOME/janus/library
setenv TCL_LIBRARY   /usr/lib/tcl8.3
setenv TK_LIBRARY    /usr/lib/tk8.3

# Compiling:
setenv IA32ROOT             /home/njd/intel/compiler60/ia32
setenv LD_LIBRARY_PATH      ${IA32ROOT}/lib

\end{verbatim}
}

For Windows, you should set the following environment variables, if
not already specified:

{\small
\begin{verbatim}
# take care of the '/' and '\'
HOME          C:\user\fuegen
JANUS_LIBRARY C:/user/fuegen/janus/library
\end{verbatim}
}

\input{files/phonesSet.tex}
\input{files/ptreeSet.tex}
\input{files/svocab.tex}
\input{files/tags.tex}
\input{files/tmSet.tex}
\input{files/topoSet.tex}
\input{files/topoTree.tex}

\section{\Jindex{db-spk}, \Jindex{db-utt}} \label{file:dbase}

Janus  contains a database   object which  stores all  the information
needed for  a particular system. An  example script to generate such a
dbase is available in \texttt{\~{ }/janus/scripts/genDBase.tcl}.

The database consists of two parts, each of which is store in a
data-file (*.dat) and an index file (*.idx):

\begin{description}
\item[db-spk] The ``speaker database''

  Every entry in  this database (corresponding to  a line in the file)
  contains information for one  ``speaker''. It should contain a field
  ``UTTS'', which lists all the  utterances (segments) which belong to
  this speaker. Also, paths to  ADC files, speaker information or warp
  factors can be stored here.

\item[db-utt] The ``utterance database''

  Every entry in this database  (corresponding to a  line in the file)
  contains  information for one   ``utterance''.  It should  contain a
  field ``SPK'', which links to the corresponding entry in the speaker
  database, a field ``UTT'', which  repeats the utterance id and further
  information (transliteration: ``TEXT'', ADC segment, ...)

\end{description}

Look at  \texttt{\~{ }/janus/scripts/genDBase.tcl} to see   how these
files can be generated from free-format data.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
