\item[AModelSet] \label{glossary:AModelSet} set of acoustic models
\item[AModel] \label{glossary:AModel} acoustic model
\item[BBILeaf] \label{glossary:BBILeaf} leaf in a BBI search tree
\item[BBINode] \label{glossary:BBINode} node in a BBI search tree
\item[BBITree] \label{glossary:BBITree} BBI search tree
\item[BMem] \label{glossary:BMem} Block Memory
\item[Cbcfg] \label{glossary:Cbcfg} configuration of a codebook
\item[CBNewParMatrixSet] \label{glossary:CBNewParMatrixSet} Set of CBNewParMatrix parameter matrices
\item[CBNewParMatrix] \label{glossary:CBNewParMatrix} Parameter matrix used by CBNew codebooks
\item[CBNewSet] \label{glossary:CBNewSet} Set of CBNew codebooks
\item[CBNewStream] \label{glossary:CBNewStream} Stream based on extended codebooks (CBNew)
\item[CBNew] \label{glossary:CBNew} Codebook using additional parameter matrices
\item[CFGArc] \label{glossary:CFGArc} A 'CFGArc' object is an arc between two nodes of a context free grammar.
\item[CFGLexiconItem] \label{glossary:CFGLexiconItem} A 'CFGLexiconItem' object is a item of a CFG lexicon.
\item[CFGLexicon] \label{glossary:CFGLexicon} A 'CFGLexicon' object is a lexicon of a Context Free Grammar.
\item[CFGNode] \label{glossary:CFGNode} A 'CFGNode' object is a node in a context free grammar.
\item[CFGParseTree] \label{glossary:CFGParseTree} A 'CFGParseTree' object is a parse tree.
\item[CFGPTItem] \label{glossary:CFGPTItem} A 'CFGPTItem' object is a item in a parse tree node.
\item[CFGPTNode] \label{glossary:CFGPTNode} A 'CFGPTNode' object is a node of a parse tree.
\item[CFGRSItem] \label{glossary:CFGRSItem} A 'CFGRSItem' object is an item in the stack of CFG rules.
\item[CFGRuleStack] \label{glossary:CFGRuleStack} A 'CFGRuleStack' object is a stack of CFG rules.
\item[CFGRule] \label{glossary:CFGRule} A 'CFGRule' object is a rule of a context free grammar.
\item[CFGSet] \label{glossary:CFGSet} A 'CFGSet' object is a set of context free grammar.
\item[CFG] \label{glossary:CFG} A 'CFG' object is a context free grammar.
\item[CMatrix] \label{glossary:CMatrix} Matrix of char values
\item[CMLLR] \label{glossary:CMLLR} Constrained MLLR
\item[CMU] \label{glossary:CMU} Carnegie Mellon University
\item[CodebookAccu] \label{glossary:CodebookAccu} a single codebook's accumulator
\item[CodebookMapItem] \label{glossary:CodebookMapItem} CodebookMapItem
\item[CodebookMap] \label{glossary:CodebookMap} CodebookMap
\item[CodebookSet] \label{glossary:CodebookSet} Set of codebooks
\item[Codebook] \label{glossary:Codebook} Codebook
\item[DBaseIdx] \label{glossary:DBaseIdx} DBase Index Object
\item[DBase] \label{glossary:DBase} DBase
\item[DCovMatrix] \label{glossary:DCovMatrix} Covariance matrix type (double)
\item[Dictionary] \label{glossary:Dictionary} Set of words
\item[DictWord] \label{glossary:DictWord} Word with tagged phone transcription
\item[DistribAccu] \label{glossary:DistribAccu} a single distribution's accumulator
\item[DistribSet] \label{glossary:DistribSet} Set of distributions
\item[DistribStream] \label{glossary:DistribStream} Distribution based stream
\item[Distrib] \label{glossary:Distrib} A single distribution
\item[DMatrix] \label{glossary:DMatrix} Matrix of double values
\item[Dscfg] \label{glossary:Dscfg} configuration of a distribution
\item[DurationSet] \label{glossary:DurationSet} A 'DurationSet' object is an array of explicite duration models.
\item[Duration] \label{glossary:Duration} explicite duration model
\item[DVector] \label{glossary:DVector} Vector of double values
\item[FArray] \label{glossary:FArray} Array of floats
\item[FBMatrix] \label{glossary:FBMatrix} Band matrix of float values
\item[FCovMatrix] \label{glossary:FCovMatrix} Covariance matrix type (float)
\item[FeatureSet] \label{glossary:FeatureSet} set of features
\item[Feature] \label{glossary:Feature} Feature
\item[FFLayer] \label{glossary:FFLayer} Single Layer in a FFNet
\item[FFLink] \label{glossary:FFLink} Single link between FFLayer's in a FFNet
\item[FFNet] \label{glossary:FFNet} General Feed Forward Multilayer Neural Network
\item[Filter] \label{glossary:Filter} LTI filter
\item[FlatFwd] \label{glossary:FlatFwd} Search: Flat Forward Module
\item[FMatrix] \label{glossary:FMatrix} Matrix of float values
\item[FMLLR] \label{glossary:FMLLR} Feature-Space Maximum Likelihood Linear Regression
\item[Forced] \label{glossary:Forced} Search: EXPERIMENTAL Beam Optimization Pass
\item[FVector] \label{glossary:FVector} Vector of float values
\item[GLat] \label{glossary:GLat} Generic Lattice (pronounced 'Gillette, everything a man ...')
\item[GSClusterSet] \label{glossary:GSClusterSet} A 'GSClusterSet' object is a cluster set on the Gaussians of a CodebookSet.
\item[HMM3gramState] \label{glossary:HMM3gramState} HMM3gram State
\item[HMM3gram] \label{glossary:HMM3gram} HMM3gram
\item[HMM] \label{glossary:HMM} An 'HMM' object contains states, transitions and acoustic references
\item[HypoList] \label{glossary:HypoList} The object HypoList contains a list of hypotheses.
\item[Hypo] \label{glossary:Hypo} Hypo is a subtype of HypoList only.
\item[IArray] \label{glossary:IArray} Array of integers
\item[Ibis] \label{glossary:Ibis} The standard one-pass decoder in Janus 5.x.
\item[IMatrix] \label{glossary:IMatrix} Matrix of integer values
\item[ISL] \label{glossary:ISL} The Interactive Systems Labs at UKA and CMU
\item[JANUS] \label{glossary:JANUS} Equivalent to JRTK, or only the janus binary
\item[Janus] \label{glossary:Janus} Equivalent to JRTK, sometimes used for pre-Ibis janus binaries
\item[janus] \label{glossary:janus} The 'janus' binary
\item[JRTk] \label{glossary:JRTk} The Janus Recognition Toolkit
\item[KeyspotterLP] \label{glossary:KeyspotterLP} A keyspotter-lp object
\item[Keyspotter] \label{glossary:Keyspotter} A keyspotter object
\item[Labelbox] \label{glossary:Labelbox} Labelbox
\item[LatNode] \label{glossary:LatNode} Lattice Node
\item[Lattice] \label{glossary:Lattice} Lattice
\item[Lat] \label{glossary:Lat} Lat
\item[LCMSet] \label{glossary:LCMSet} set of left context models
\item[LCM] \label{glossary:LCM} left context model
\item[LDAClass] \label{glossary:LDAClass} LDA class
\item[LDA] \label{glossary:LDA} LDA
\item[Lh] \label{glossary:Lh} a codebook-likelihoods accumulator
\item[LingKS] \label{glossary:LingKS} Generic Linguistic Knowledge Source:
\item[List] \label{glossary:List} List of indexed items
\item[LModelBackoffItem] \label{glossary:LModelBackoffItem} Language Model Selection
\item[LModelBackoff] \label{glossary:LModelBackoff} Language Model Selection
\item[LModelIntItem] \label{glossary:LModelIntItem} Language Model interpolation
\item[LModelInt] \label{glossary:LModelInt} Language Model Intper
\item[LModelItem] \label{glossary:LModelItem} 3G Language Model Item
\item[LModelLongItem] \label{glossary:LModelLongItem} Mgram Language Model Item
\item[LModelLong] \label{glossary:LModelLong} Mgram Language Model
\item[LModelMapItem] \label{glossary:LModelMapItem} Language Model mapping
\item[LModelMap] \label{glossary:LModelMap} Language Model Mapper
\item[LModel] \label{glossary:LModel} 3G Language Model
\item[Lm] \label{glossary:Lm} The object Lm contains a language model.
\item[LookAhead] \label{glossary:LookAhead} LookAhead (fast match) part for tree and flat search
\item[LTree] \label{glossary:LTree} Language-Model Look-Ahead object (Lexical tree)
\item[MAM] \label{glossary:MAM} Model-Based Acoustic Mapping
\item[MAP] \label{glossary:MAP} Maximum A-Posteriori Estimation
\item[MetaLMElem] \label{glossary:MetaLMElem} Meta language model element (sub-LM).
\item[MetaLMItem] \label{glossary:MetaLMItem} Meta language model item.
\item[MetaLM] \label{glossary:MetaLM} Meta language model: flexible LM using sub-LMs.
\item[MicvSet] \label{glossary:MicvSet} Set of Mixture of Inverse CoVariances Codebooks
\item[MicvStream] \label{glossary:MicvStream} Stream based on MIC codebooks (Micv)
\item[MLAdaptItem] \label{glossary:MLAdaptItem} MLAdaptItem
\item[MLAdapt] \label{glossary:MLAdapt} Maximum Likelihood Adaptation
\item[MLE] \label{glossary:MLE} Maximum Likelihood Estimation
\item[MLLR] \label{glossary:MLLR} Maximum Likelihood Linear Regression
\item[MMIE] \label{glossary:MMIE} Maximum Mutual Information Estimation
\item[ModalitySet] \label{glossary:ModalitySet} A 'ModalitySet' object is a set of modalities.
\item[Modality] \label{glossary:Modality} A 'Modality' object answers a question about the modality of a recording.
\item[ModelArray] \label{glossary:ModelArray} Array of models.
\item[NGramLMItem] \label{glossary:NGramLMItem} N-gram Language Model Item
\item[NGramLMSubs] \label{glossary:NGramLMSubs} N-gram Language Model Substitution Item
\item[NGramLM] \label{glossary:NGramLM} N-gram Language Model
\item[PathItemList] \label{glossary:PathItemList} PathItemList
\item[PathItem] \label{glossary:PathItem} PathItem
\item[Path] \label{glossary:Path} A 'Path' object is filled by a forced alignment function and is used by training functions
\item[PHMMSet] \label{glossary:PHMMSet} set of phone hidden markov models
\item[PHMM] \label{glossary:PHMM} phone hidden markov model
\item[PhoneGraph] \label{glossary:PhoneGraph} PhoneGraph
\item[PhonesSet] \label{glossary:PhonesSet} A 'PhonesSet' object is a set of 'Phones' objects.
\item[Phones] \label{glossary:Phones} A 'Phones' object is an array of strings, each of which is a phoneme.
\item[Phone] \label{glossary:Phone} Phone
\item[PhraseLMItem] \label{glossary:PhraseLMItem} Phrase language model item.
\item[PhraseLM] \label{glossary:PhraseLM} This module takes a LM and adds phrases (aka. multi-words) to it.
\item[PTreeNode] \label{glossary:PTreeNode} PTreeNode
\item[PTreeSet] \label{glossary:PTreeSet} A 'PTreeSet' object is a set of polyphone context trees.
\item[PTree] \label{glossary:PTree} Polyphonic Tree
\item[QuestionSet] \label{glossary:QuestionSet} A 'QuestionSet' object is a set of characteristic function definitions and a set of questionSet.
\item[Question] \label{glossary:Question} A 'Question' object is a definition of a single question.
\item[RCMSet] \label{glossary:RCMSet} set of right context models
\item[RCM] \label{glossary:RCM} right context model
\item[RewriteSet] \label{glossary:RewriteSet} Set of rewrite rules
\item[Rewrite] \label{glossary:Rewrite} Rewrite Rule
\item[SampleSetClass] \label{glossary:SampleSetClass} a class in a SampleSet
\item[SampleSet] \label{glossary:SampleSet} containers for samples
\item[Search] \label{glossary:Search} Search Module
\item[SenoneSet] \label{glossary:SenoneSet} Set of senones
\item[SenoneTag] \label{glossary:SenoneTag} SenoneTag
\item[Senone] \label{glossary:Senone} Senone
\item[SignalAdapt] \label{glossary:SignalAdapt} Signal Adaption
\item[SMem] \label{glossary:SMem} Search Memory Manager
\item[SNode] \label{glossary:SNode} Search Root
\item[SPass] \label{glossary:SPass} Single Pass Decoder
\item[SRoot] \label{glossary:SRoot} Search Root
\item[STab] \label{glossary:STab} Backpointer table
\item[StateGraph] \label{glossary:StateGraph} StateGraph
\item[StateTable] \label{glossary:StateTable} A 'StateTable' object is a matrix for looking up distribution indices.
\item[StreamNormItem] \label{glossary:StreamNormItem} A stream normalizer
\item[STree] \label{glossary:STree} Search Tree
\item[SVector] \label{glossary:SVector} Vector of short values
\item[SVMap] \label{glossary:SVMap} Search Vocabulary Mapper
\item[SVocab] \label{glossary:SVocab} Search Vocabulary
\item[SWord] \label{glossary:SWord} Search Vocabulary Word
\item[Tags] \label{glossary:Tags} A 'Tags' object is an array of strings.
\item[Tag] \label{glossary:Tag} Tag
\item[TextGraph] \label{glossary:TextGraph} Text Graph
\item[TmSet] \label{glossary:TmSet} A TmSet is a set of state transition model objects (Tm) 
\item[TopoSet] \label{glossary:TopoSet} A 'TopoSet' object is a set of different topologies.
\item[Topo] \label{glossary:Topo} A 'Topo' object is a definition of a single topology description.
\item[TreeFwd] \label{glossary:TreeFwd} Search: Tree Forward Module
\item[TreeNode] \label{glossary:TreeNode} TreeNode
\item[Tree] \label{glossary:Tree} A 'Tree' object is an allophone clustering tree.
\item[UKA] \label{glossary:UKA} Universit\"at Karlsruhe (TH)
\item[Vocab] \label{glossary:Vocab} A Vocab is the list of words the recognizer can recognize
\item[WordGraph] \label{glossary:WordGraph} WordGraph
\item[WordList] \label{glossary:WordList} WordList to communicate between tree and flat pass of searches
\item[Word] \label{glossary:Word} Word with tagged phone transcription
\item[XCMSet] \label{glossary:XCMSet} set of left/right context models
\item[XCM] \label{glossary:XCM} left and right context model
\item[XWModelSet] \label{glossary:XWModelSet} set of blah
\item[XWModel] \label{glossary:XWModel} blah
