\JaddGloss{LingKS}{Generic Linguistic Knowledge Source:}

\JaddGloss{XCM}{left and right context model}

\JaddGloss{FlatFwd}{Search: Flat Forward Module}

\JaddGloss{ModelArray}{Array of models.}

\JaddGloss{Keyspotter}{A keyspotter object}

\JaddGloss{DurationSet}{A 'DurationSet' object is an array of explicite duration models.}

\JaddGloss{CBNewStream}{Stream based on extended codebooks (CBNew)}

\JaddGloss{BBINode}{node in a BBI search tree}

\JaddGloss{LTree}{Language-Model Look-Ahead object (Lexical tree)}

\JaddGloss{XCMSet}{set of left/right context models}

\JaddGloss{Word}{Word with tagged phone transcription}

\JaddGloss{Cbcfg}{configuration of a codebook}

\JaddGloss{CFGRuleStack}{A 'CFGRuleStack' object is a stack of CFG rules.}

\JaddGloss{SampleSet}{containers for samples}

\JaddGloss{CBNew}{Codebook using additional parameter matrices}

\JaddGloss{ModalitySet}{A 'ModalitySet' object is a set of modalities.}

\JaddGloss{DVector}{Vector of double values}

\JaddGloss{GSClusterSet}{A 'GSClusterSet' object is a cluster set on the Gaussians of a CodebookSet.}

\JaddGloss{PTree}{Polyphonic Tree}

\JaddGloss{BMem}{Block Memory}

\JaddGloss{CFGLexicon}{A 'CFGLexicon' object is a lexicon of a Context Free Grammar.}

\JaddGloss{HMM}{An 'HMM' object contains states, transitions and acoustic references}

\JaddGloss{AModel}{acoustic model}

\JaddGloss{Rewrite}{Rewrite Rule}

\JaddGloss{CodebookSet}{Set of codebooks}

\JaddGloss{CBNewParMatrixSet}{Set of CBNewParMatrix parameter matrices}

\JaddGloss{FFNet}{General Feed Forward Multilayer Neural Network}

\JaddGloss{Vocab}{A Vocab is the list of words the recognizer can recognize}

\JaddGloss{FMatrix}{Matrix of float values}

\JaddGloss{CodebookMapItem}{CodebookMapItem}

\JaddGloss{PTreeSet}{A 'PTreeSet' object is a set of polyphone context trees.}

\JaddGloss{LModel}{3G Language Model}

\JaddGloss{BBILeaf}{leaf in a BBI search tree}

\JaddGloss{RCMSet}{set of right context models}

\JaddGloss{PHMMSet}{set of phone hidden markov models}

\JaddGloss{SVMap}{Search Vocabulary Mapper}

\JaddGloss{Dscfg}{configuration of a distribution}

\JaddGloss{LModelBackoffItem}{Language Model Selection}

\JaddGloss{PathItemList}{PathItemList}

\JaddGloss{DictWord}{Word with tagged phone transcription}

\JaddGloss{Question}{A 'Question' object is a definition of a single question.}

\JaddGloss{MLAdaptItem}{MLAdaptItem}

\JaddGloss{CodebookAccu}{a single codebook's accumulator}

\JaddGloss{CFGParseTree}{A 'CFGParseTree' object is a parse tree.}

\JaddGloss{CFGRSItem}{A 'CFGRSItem' object is an item in the stack of CFG rules.}

\JaddGloss{HypoList}{The object HypoList contains a list of hypotheses.}

\JaddGloss{SenoneTag}{SenoneTag}

\JaddGloss{QuestionSet}{A 'QuestionSet' object is a set of characteristic function definitions and a set of questionSet.}

\JaddGloss{DBaseIdx}{DBase Index Object}

\JaddGloss{Feature}{Feature}

\JaddGloss{Lh}{a codebook-likelihoods accumulator}

\JaddGloss{SampleSetClass}{a class in a SampleSet}

\JaddGloss{BBITree}{BBI search tree}

\JaddGloss{CFGNode}{A 'CFGNode' object is a node in a context free grammar.}

\JaddGloss{SVocab}{Search Vocabulary}

\JaddGloss{Dictionary}{Set of words}

\JaddGloss{DBase}{DBase}

\JaddGloss{GLat}{Generic Lattice (pronounced 'Gillette, everything a man ...')}

\JaddGloss{MetaLM}{Meta language model: flexible LM using sub-LMs.}

\JaddGloss{LCMSet}{set of left context models}

\JaddGloss{SNode}{Search Root}

\JaddGloss{CFGLexiconItem}{A 'CFGLexiconItem' object is a item of a CFG lexicon.}

\JaddGloss{Lm}{The object Lm contains a language model.}

\JaddGloss{StateTable}{A 'StateTable' object is a matrix for looking up distribution indices.}

\JaddGloss{DCovMatrix}{Covariance matrix type (double)}

\JaddGloss{PhonesSet}{A 'PhonesSet' object is a set of 'Phones' objects.}

\JaddGloss{RCM}{right context model}

\JaddGloss{PHMM}{phone hidden markov model}

\JaddGloss{Phone}{Phone}

\JaddGloss{MicvSet}{Set of Mixture of Inverse CoVariances Codebooks}

\JaddGloss{DistribAccu}{a single distribution's accumulator}

\JaddGloss{FBMatrix}{Band matrix of float values}

\JaddGloss{Phones}{A 'Phones' object is an array of strings, each of which is a phoneme.}

\JaddGloss{KeyspotterLP}{A keyspotter-lp object}

\JaddGloss{TreeNode}{TreeNode}

\JaddGloss{IMatrix}{Matrix of integer values}

\JaddGloss{CBNewParMatrix}{Parameter matrix used by CBNew codebooks}

\JaddGloss{LModelBackoff}{Language Model Selection}

\JaddGloss{Labelbox}{Labelbox}

\JaddGloss{Distrib}{A single distribution}

\JaddGloss{CFGPTItem}{A 'CFGPTItem' object is a item in a parse tree node.}

\JaddGloss{MLAdapt}{Maximum Likelihood Adaptation}

\JaddGloss{PhraseLM}{This module takes a LM and adds phrases (aka. multi-words) to it.}

\JaddGloss{HMM3gram}{HMM3gram}

\JaddGloss{List}{List of indexed items}

\JaddGloss{Tag}{Tag}

\JaddGloss{CFGArc}{A 'CFGArc' object is an arc between two nodes of a context free grammar.}

\JaddGloss{TopoSet}{A 'TopoSet' object is a set of different topologies.}

\JaddGloss{SVector}{Vector of short values}

\JaddGloss{MetaLMItem}{Meta language model item.}

\JaddGloss{StreamNormItem}{A stream normalizer}

\JaddGloss{CFGRule}{A 'CFGRule' object is a rule of a context free grammar.}

\JaddGloss{XWModel}{blah}

\JaddGloss{WordList}{WordList to communicate between tree and flat pass of searches}

\JaddGloss{IArray}{Array of integers}

\JaddGloss{FFLayer}{Single Layer in a FFNet}

\JaddGloss{Lat}{Lat}

\JaddGloss{DMatrix}{Matrix of double values}

\JaddGloss{FVector}{Vector of float values}

\JaddGloss{FFLink}{Single link between FFLayer's in a FFNet}

\JaddGloss{LModelMapItem}{Language Model mapping}

\JaddGloss{STree}{Search Tree}

\JaddGloss{Forced}{Search: EXPERIMENTAL Beam Optimization Pass}

\JaddGloss{StateGraph}{StateGraph}

\JaddGloss{MicvStream}{Stream based on MIC codebooks (Micv)}

\JaddGloss{FCovMatrix}{Covariance matrix type (float)}

\JaddGloss{XWModelSet}{set of blah}

\JaddGloss{LModelLongItem}{Mgram Language Model Item}

\JaddGloss{PathItem}{PathItem}

\JaddGloss{FArray}{Array of floats}

\JaddGloss{NGramLM}{N-gram Language Model}

\JaddGloss{Duration}{explicite duration model}

\JaddGloss{PTreeNode}{PTreeNode}

\JaddGloss{SRoot}{Search Root}

\JaddGloss{LatNode}{Lattice Node}

\JaddGloss{TextGraph}{Text Graph}

\JaddGloss{CFG}{A 'CFG' object is a context free grammar.}

\JaddGloss{Hypo}{Hypo is a subtype of HypoList only.}

\JaddGloss{LModelInt}{Language Model Intper}

\JaddGloss{LookAhead}{LookAhead (fast match) part for tree and flat search}

\JaddGloss{Senone}{Senone}

\JaddGloss{SignalAdapt}{Signal Adaption}

\JaddGloss{TreeFwd}{Search: Tree Forward Module}

\JaddGloss{LDA}{LDA}

\JaddGloss{SPass}{Single Pass Decoder}

\JaddGloss{SMem}{Search Memory Manager}

\JaddGloss{Topo}{A 'Topo' object is a definition of a single topology description.}

\JaddGloss{PhraseLMItem}{Phrase language model item.}

\JaddGloss{NGramLMSubs}{N-gram Language Model Substitution Item}

\JaddGloss{CBNewSet}{Set of CBNew codebooks}

\JaddGloss{CFGSet}{A 'CFGSet' object is a set of context free grammar.}

\JaddGloss{LCM}{left context model}

\JaddGloss{SenoneSet}{Set of senones}

\JaddGloss{HMM3gramState}{HMM3gram State}

\JaddGloss{Lattice}{Lattice}

\JaddGloss{WordGraph}{WordGraph}

\JaddGloss{Codebook}{Codebook}

\JaddGloss{SWord}{Search Vocabulary Word}

\JaddGloss{LDAClass}{LDA class}

\JaddGloss{Tags}{A 'Tags' object is an array of strings.}

\JaddGloss{Tree}{A 'Tree' object is an allophone clustering tree.}

\JaddGloss{CMatrix}{Matrix of char values}

\JaddGloss{FeatureSet}{set of features}

\JaddGloss{STab}{Backpointer table}

\JaddGloss{CFGPTNode}{A 'CFGPTNode' object is a node of a parse tree.}

\JaddGloss{MetaLMElem}{Meta language model element (sub-LM).}

\JaddGloss{LModelMap}{Language Model Mapper}

\JaddGloss{Modality}{A 'Modality' object answers a question about the modality of a recording.}

\JaddGloss{LModelItem}{3G Language Model Item}

\JaddGloss{PhoneGraph}{PhoneGraph}

\JaddGloss{CodebookMap}{CodebookMap}

\JaddGloss{NGramLMItem}{N-gram Language Model Item}

\JaddGloss{LModelLong}{Mgram Language Model}

\JaddGloss{Path}{A 'Path' object is filled by a forced alignment function and is used by training functions}

\JaddGloss{TmSet}{A TmSet is a set of state transition model objects (Tm) }

\JaddGloss{DistribStream}{Distribution based stream}

\JaddGloss{DistribSet}{Set of distributions}

\JaddGloss{Search}{Search Module}

\JaddGloss{AModelSet}{set of acoustic models}

\JaddGloss{Filter}{LTI filter}

\JaddGloss{RewriteSet}{Set of rewrite rules}

\JaddGloss{LModelIntItem}{Language Model interpolation}

